Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density \thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-05-31 manuscript.tex
sec 4 updates

\xavier{In this section, we simulate the effect on the CCF parameters of an equatorial spot of size 1\% relative to the visible stellar hemisphere. The spot is face on when the phase equals to 0. Note that this is an extremely big spot for the Sun, as in general big spots are more in the regime of 0.1\%.
In Fig.~\ref{fig:spot}, we shows the barycentric variation of the CCF induced by this simulated spot. Contrary to the case of the faculae seen before, for the spots, all the different estimates of the CCF barycenter have exactly the same shape in variation. The amplitude for SN mean RV is however slightly smaller.}

Fig.~\ref{fig:spot.corr} shows the correlations between the asymmetry parameters and the different estimates for the CCF barycenter: SN mean RV, SN median RV and RV. \xavier{The correlation between $\gamma$ and SN median RV is the strongest with a $R=0.94$, followed then by the correlation BIS SPAN -RV and $\gamma$-SN mean RV, with $R=0.86$. Regarding the correlation between the width and the CCF barycenter, we note that the variation is seen as a circle in this parameter space and therefore no correlation is observed. Once again, like in the case of the faculae, we see that some parameters of the SN gives stronger correlation than when using the Normal parameters.}

>>>>

In this section, we consider the effects on the CCF parameters of an equatorial spot of size 1\% relative to the visible stellar hemisphere. The spot is face on when the phase equals to 0. Note that this is a large spot for the Sun, as in general large spots are more in the regime of 0.1\%.\jessi{Can we add a reference for the previous statement?}
In Fig.~\ref{fig:spot}, we shows the barycentric variation of the CCF induced by this simulated spot. In contrast to the case of the facula, all the different estimates of the CCF barycenter for the spot have the same shape in variation. The amplitude for SN mean RV is however slightly smaller.

Fig.~\ref{fig:spot.corr} shows the correlations between the asymmetry parameters and the different estimates for the CCF barycenter (i.e. the SN mean RV, SN median RV and RV). The correlation between $\gamma$ and SN median RV is the strongest with a $R=0.94$, followed by the correlation BIS SPAN - RV and $\gamma$ - SN mean RV, with $R=0.86$. \jessi{Do the previous numbers need updating?}  Regarding the correlation between the width and the CCF barycenter, we note that the variation is seen as a circle in this parameter space and therefore no correlation is observed. Once again, like in the case of the facula, we see that some parameters of the SN gives stronger correlations than when using the Normal parameters.
